### 2018-12-31 Sections/intro_to_QM.tex
indexing

	\item Measurement collapse: the measurement of a quantum system changes its state in general, \textit{collapsing} it to the state corresponding to the measurement outcome\footnote{An open and intuitively confusing conundrum in quantum theory is to resolve the question of what exactly it is that constitutes `measurement' -- the \textit{measurement paradox}\index{Measurement paradox}. Given that all quantum evolution is supposed to be governed by unitary dynamics, whereas measurements are not, at what point in physical reality does an operation transition from one to the other? This is an extremely important open question, particularly from the perspective of quantum foundations and the philosophy of physics. This has led to the emergence of countless theories for the interpretation of quantum mechanics\index{Interpretation of quantum mechanics}, which is an essentially untestable field of research, more akin to fundamentalist religious movements than physical science. However, the resolution is largely unimportant in a practical technological context, where it suffices to define `measurement' as being `when quantum information becomes classical information', e.g once we are able to read it off a measurement device's LCD screen!}.\index{Measurement!Collapse}
	\item Non-determinism: quantum systems exhibit genuine non-determinism, associated with the randomness of the measurement collapse\index{Measurement!Collapse} process\footnote{When we say `random' we \textit{really} mean random, not `quasi-random but actually deterministic'\index{Quasi-randomness}. This true randomness is another of the unique and surprising features of quantum mechanics. Conversely to classical physics, quantum mechanics is inherently and provably non-deterministic! Specifically, it has been proven theoretically \cite{bib:BellNoHiddenVariables} that so-called `hidden variable theories'\index{Hidden variable theories} are incompatible with quantum physics, which rules out any form of quasi-randomness and mandates true randomness.}.\index{Non-determinism}

@@

The most fundamental mathematical object in representing quantum systems is the \textit{state vector}, a vector representation for the quantum wave-function\index{Wave-function}.

@@

For two generic state vectors, supported by the same basis,
\begin{align}
	\ket\psi = \sum_n \alpha_n \ket{n},\nonumber\\
	\ket\phi = \sum_n \beta_n \ket{n},
\end{align}
the \textit{overlap}\index{Overlap} between them is defined as,
\begin{align}
\braket{\psi|\phi} = \sum_n \alpha_n\beta_n^*,
\end{align}
which is mathematically equivalent to their vector dot product\index{Dot product}. The magnitude of the overlap of two quantum states lies in the range,
\begin{align}
	0\leq|\braket{\psi|\phi}|\leq 1,
\end{align}
where \mbox{$|\braket{\psi|\phi}|=0$} indicates that the two states were orthogonal, and \mbox{$|\braket{\psi|\phi}|=1$} implies they are identical (up to an irrelevant global phase\index{Global phase}\footnote{In quantum mechanics, all quantum states are physically invariant under the introduction of a \textit{global} phase-factor, i.e \mbox{$\ket\psi\to e^{i\theta}\ket\psi$}. Thus, global phases may always be safely ignored without changing the underlying physical reality. This most certainly does not apply to \textit{local} phases, which are a part of physical reality, and critically affect interference dynamics.}). The object $\braket{\cdot|\cdot}$ is referred to as a \textit{braket}\footnote{We never quite appreciated the corny sense of humour of the author of the terms \textit{bra}, \textit{ket}, and \textit{braket}. But somehow it stuck.}\index{Braket}. The normalisation condition from Eq.~(\ref{eq:state_norm_cond}) can therefore equivalently be written,
\begin{align}\index{Normalisation}
\braket{\psi|\psi} = 1.	
\end{align}
Owing to the cyclic property of the trace operator\index{Trace operator}, it follows that the trace,
\begin{align}
\mathrm{tr}(\ket\psi\bra\phi)=\braket{\psi|\phi},	
\end{align}
is a state overlap. This quantity has the useful intuitive interpretation as the \textit{distinguishability}\index{Distinguishability} between quantum states, which plays an important role in measurement theory and the theory of quantum information. It is also widely used to characterise the quality of quantum experiments, as a way of comparing quantum states prepared in the lab with the ideal states obtained from the theory.

@@

More generally, we may also have states of the form,
\begin{align}
\ket\psi_{A,B} =\sum_{m,n} \lambda_{m,n}\ket{m}_A\otimes\ket{n}_B,
\end{align}
where in general $\lambda_{m,n}$ may not be separable as,
\begin{align}
\lambda_{m,n}=\alpha_m\beta_n.
\end{align}
In this case no complete physical description exists for either subsystem in isolation -- they may only be described collectively. Now the state is said to be \textit{entangled}\index{Entanglement}, a uniquely quantum class of physical states with no classical analogue. The simplest and best-known example is the \textit{Bell state}\index{Bell states} on two qubits,
\begin{align}\label{eq:bell_state_vec_def}
\ket\Phi^+_{A,B} &= \frac{1}{\sqrt{2}}\begin{pmatrix}
  1\\
  0\\
  0\\
  1
\end{pmatrix}\nonumber\\
&= \frac{1}{\sqrt{2}}(\ket{0}_A\ket{0}_B+\ket{1}_A\ket{1}_B).
\end{align}
It's obvious upon inspection that the Bell state cannot be written in separable form,
\begin{align}
	\ket\Phi^+_{A,B} \neq \ket\psi_A \otimes \ket\phi_B,
\end{align}
and is hence entangled.

@@

In quantum mechanics the discrete-time evolution of an $N$-dimensional state is given by arbitrary \mbox{$N\times N$}-dimensional unitary transformations\index{Unitary operators}, $\mathrm{U}(N)$, which satisfy,
\begin{align}
\hat{U}^\dag\hat{U}=\hat\openone.	
\end{align}

@@

The above formalism describes quantum evolution by acting the unitary operator on the quantum state directly,
\begin{align}
\ket{\psi'} = \hat{U}\ket\psi.
\end{align}
This is known as the \textit{Schr{\" o}dinger picture}\index{Schr{\" o}dinger picture}. An alternate, but entirely mathematically equivalent approach is the \textit{Heisenberg picture}\index{Heisenberg picture}, whereby we evolve the operators acting upon a state, rather than the state itself. Now the operator evolution is described by conjugating the operators with the unitary operator describing the evolution. That is, representing the quantum state in terms of some operator $\hat{o}$, the operator evolution proceeds as,
\begin{align}
	\hat{o}' = \hat{U}\hat{o}\hat{U}^\dag.
\end{align}

@@

We define a measurement \textit{observable}\index{Observable} as an operator $\hat{O}$ acting on a state-space, with eigenvalues $O_i$ over some range of $i$. The eigenvalues $O_i$ denote the allowed values of the measurement outcome for the associated eigenstate, which corresponds to the projected post-measurement state. The statistical expectation value\index{Expectation value} of these measurement outcomes for a given state $\ket\psi$ may now be obtained as the expectation value of the observable,
\begin{align}
	\braket{\hat{O}} = \braket{\psi|\hat{O}|\psi},
\end{align}
and their variance\index{Variance} by,
\begin{align}
	\braket{\hat{O}^2} - \braket{\hat{O}}^2.
\end{align}
Both of these are in the limit of an infinite number of independent trials of the measurement performed on identical copies of the state.

@@

Next we will apply the so-called Hadamard gate\index{Hadamard gate}, given by the \mbox{$2\times 2$} unitary matrix,
\begin{align}
\hat{H} = \frac{1}{\sqrt{2}}\begin{pmatrix}
  1 & 1 \\
  1 & -1
\end{pmatrix}.
\end{align}

>>>>

	\item Measurement collapse: the measurement of a quantum system changes its state in general, \textit{collapsing} it to the state corresponding to the measurement outcome\footnote{An open and intuitively confusing conundrum in quantum theory is to resolve the question of what exactly it is that constitutes `measurement' -- the \textit{measurement paradox}\index{Measurement!Paradox}. Given that all quantum evolution is supposed to be governed by unitary dynamics, whereas measurements are not, at what point in physical reality does an operation transition from one to the other? This is an extremely important open question, particularly from the perspective of quantum foundations and the philosophy of physics. This has led to the emergence of countless theories for the interpretation of quantum mechanics\index{Interpretation of quantum mechanics}, which is an essentially untestable field of research, more akin to fundamentalist religious movements than physical science. However, the resolution is largely unimportant in a practical technological context, where it suffices to define `measurement' as being `when quantum information becomes classical information', e.g once we are able to read it off a measurement device's LCD screen!}.\index{Measurement!Collapse}
	\item Non-determinism: quantum systems exhibit genuine non-determinism, associated with the randomness of the measurement collapse\index{Measurement!Collapse} process\footnote{When we say `random' we \textit{really} mean random, not `quasi-random but actually deterministic'\index{Quasi-randomness}. This true randomness is another of the unique and surprising features of quantum mechanics. Conversely to classical physics, quantum mechanics is inherently and provably non-deterministic! Specifically, it has been proven theoretically \cite{bib:BellNoHiddenVariables} that so-called `hidden variable theories'\index{Hidden variable theories} are incompatible with quantum physics, which rules out any form of quasi-randomness and mandates true randomness.}.\index{Non-determinism of quantum mechanics}

@@

The most fundamental mathematical object in representing quantum systems is the \textit{state vector}, a vector representation for the quantum wave-function\index{Wave-functions}.

@@

For two generic state vectors, supported by the same basis,
\begin{align}
	\ket\psi = \sum_n \alpha_n \ket{n},\nonumber\\
	\ket\phi = \sum_n \beta_n \ket{n},
\end{align}
the \textit{overlap}\index{State!Overlap} between them is defined as,
\begin{align}
\braket{\psi|\phi} = \sum_n \alpha_n\beta_n^*,
\end{align}
which is mathematically equivalent to their vector dot product\index{Dot product}. The magnitude of the overlap of two quantum states lies in the range,
\begin{align}
	0\leq|\braket{\psi|\phi}|\leq 1,
\end{align}
where \mbox{$|\braket{\psi|\phi}|=0$} indicates that the two states were orthogonal, and \mbox{$|\braket{\psi|\phi}|=1$} implies they are identical (up to an irrelevant global phase\index{Global phase}\footnote{In quantum mechanics, all quantum states are physically invariant under the introduction of a \textit{global} phase-factor, i.e \mbox{$\ket\psi\to e^{i\theta}\ket\psi$}. Thus, global phases may always be safely ignored without changing the underlying physical reality. This most certainly does not apply to \textit{local} phases, which are a part of physical reality, and critically affect interference dynamics.}). The object $\braket{\cdot|\cdot}$ is referred to as a \textit{braket}\footnote{We never quite appreciated the corny sense of humour of the author of the terms \textit{bra}, \textit{ket}, and \textit{braket}. But somehow it stuck.}\index{Braket}. The normalisation condition from Eq.~(\ref{eq:state_norm_cond}) can therefore equivalently be written,
\begin{align}\index{Normalisation}
\braket{\psi|\psi} = 1.	
\end{align}
Owing to the cyclic property of the trace operator\index{Trace operator}, it follows that the trace,
\begin{align}
\mathrm{tr}(\ket\psi\bra\phi)=\braket{\psi|\phi},	
\end{align}
is a state overlap. This quantity has the useful intuitive interpretation as the \textit{distinguishability}\index{Distinguishability} between quantum states, which plays an important role in measurement theory and the theory of quantum information. It is also widely used to characterise the quality of quantum experiments, as a way of comparing quantum states prepared in the lab with the ideal states obtained from the theory.

@@

More generally, we may also have states of the form,
\begin{align}
\ket\psi_{A,B} =\sum_{m,n} \lambda_{m,n}\ket{m}_A\otimes\ket{n}_B,
\end{align}
where in general $\lambda_{m,n}$ may not be separable as,
\begin{align}
\lambda_{m,n}=\alpha_m\beta_n.
\end{align}
In this case no complete physical description exists for either subsystem in isolation -- they may only be described collectively. Now the state is said to be \textit{entangled}\index{Entanglement}, a uniquely quantum class of physical states with no classical analogue. The simplest and best-known example is the \textit{Bell state}\index{Bell!States} on two qubits,
\begin{align}\label{eq:bell_state_vec_def}
\ket\Phi^+_{A,B} &= \frac{1}{\sqrt{2}}\begin{pmatrix}
  1\\
  0\\
  0\\
  1
\end{pmatrix}\nonumber\\
&= \frac{1}{\sqrt{2}}(\ket{0}_A\ket{0}_B+\ket{1}_A\ket{1}_B).
\end{align}
It's obvious upon inspection that the Bell state cannot be written in separable form,
\begin{align}
	\ket\Phi^+_{A,B} \neq \ket\psi_A \otimes \ket\phi_B,
\end{align}
and is hence entangled.

@@

In quantum mechanics the discrete-time evolution of an $N$-dimensional state is given by arbitrary \mbox{$N\times N$}-dimensional unitary transformations\index{Unitary!Operators}, $\mathrm{U}(N)$, which satisfy,
\begin{align}
\hat{U}^\dag\hat{U}=\hat\openone.	
\end{align}

@@

The above formalism describes quantum evolution by acting the unitary operator on the quantum state directly,
\begin{align}
\ket{\psi'} = \hat{U}\ket\psi.
\end{align}
This is known as the \textit{Schr{\" o}dinger picture}\index{Schr{\" o}dinger!Picture}. An alternate, but entirely mathematically equivalent approach is the \textit{Heisenberg picture}\index{Heisenberg!Picture}, whereby we evolve the operators acting upon a state, rather than the state itself. Now the operator evolution is described by conjugating the operators with the unitary operator describing the evolution. That is, representing the quantum state in terms of some operator $\hat{o}$, the operator evolution proceeds as,
\begin{align}
	\hat{o}' = \hat{U}\hat{o}\hat{U}^\dag.
\end{align}

@@

We define a measurement \textit{observable}\index{Observables} as an operator $\hat{O}$ acting on a state-space, with eigenvalues $O_i$ over some range of $i$. The eigenvalues $O_i$ denote the allowed values of the measurement outcome for the associated eigenstate, which corresponds to the projected post-measurement state. The statistical expectation value\index{Expectation values} of these measurement outcomes for a given state $\ket\psi$ may now be obtained as the expectation value of the observable,
\begin{align}
	\braket{\hat{O}} = \braket{\psi|\hat{O}|\psi},
\end{align}
and their variance\index{Variance} by,
\begin{align}
	\braket{\hat{O}^2} - \braket{\hat{O}}^2.
\end{align}
Both of these are in the limit of an infinite number of independent trials of the measurement performed on identical copies of the state.

@@

Next we will apply the so-called Hadamard gate\index{Hadamard!Gate}, given by the \mbox{$2\times 2$} unitary matrix,
\begin{align}
\hat{H} = \frac{1}{\sqrt{2}}\begin{pmatrix}
  1 & 1 \\
  1 & -1
\end{pmatrix}.
\end{align}

### 2018-12-31 Sections/intro_to_QO.tex
Schroedinger vs Heisenberg pictures
indexing

\section{Introduction to quantum optics}\index{Quantum optics}

@@

The most basic optical quantum state comprising photons is the \textit{photon-number state}\index{Photon-number!State} or \textit{Fock state}. These states form a discrete basis, labelled by the integer number of photons in the state,
\begin{align}
\ket{n},\,n\in\mathbb{Z}^+.	
\end{align}
The special case of $\ket{0}$ is referred to as the \textit{vacuum state}\index{Vacuum state}, since it contains no photons.

@@

\subsubsection{Creation \& annihilation operators}

@@

In the CV picture, instead of representing states using photonic creation operators, we express them in terms of the \textit{position} ($\hat x$)\index{Position operator} and \textit{momentum} ($\hat p$)\index{Momentum operator} operators, which are related to the creation and annihilation operators via,
\begin{align}
\hat x &=    \sqrt{\frac{\hbar}{2 \omega}}(\hat a + \hat a^\dag), \nonumber \\
\hat p &= -i \sqrt{\frac{\hbar  \omega}{2}}(\hat a - \hat a^\dag), 
\end{align}
where $\omega$ is the optical frequency\index{Optical!Frequency}. These operators obey the commutation relation\index{Commutation relations},
\begin{align}
[\hat x, \hat p] = i \hbar,
\end{align}
and satisfy the eigenvalue relations with the position and momentum eigenstates,
\begin{align}
\hat{x}\ket{x} &= x\ket{x},\nonumber\\
\hat{p}\ket{p} &= p\ket{p}.	
\end{align}
These eigenstates satisfy the completeness relations,
\begin{align}
\int_{-\infty}^\infty \ket{x}\bra{x}\,dx &= \hat\openone,\nonumber\\
\int_{-\infty}^\infty \ket{p}\bra{p}\,dp &	= \hat\openone.
\end{align}

The position and momentum operators represent the \textit{quadratures}\index{Quadratures} of a mode, and correspond to the real and imaginary components of a harmonic oscillator's\index{Harmonic oscillator} amplitude.

@@

\subsubsection{Position \& momentum representations}\index{Position representation}\index{Momentum representation}

The \textit{position representation} of an optical state corresponds to expressing a state vector $\ket{\psi}$ in the position basis\index{Position basis representation},
\begin{align}
\ket{\psi} = \int \psi(x)\ket{x}\, dx.
\end{align}

Here the wave-function\index{Wave-functions} in the position representation\index{Position basis representation} is defined as,
\begin{align}
\psi(x) = \braket{x|\psi}.
\end{align}
The state can similarly be expressed via a \textit{momentum representation}\index{Momentum basis representation},
\begin{align}
	\ket\psi = \int {\tilde\psi}(p) \ket{p}\, dp,
\end{align}s
with wave-function\index{Wave-functions},
\begin{align}
	{\tilde\psi}(p) = \braket{p|\psi},\nonumber\\
\end{align}

>>>>

\section{Introduction to quantum optics}\index{Quantum optics}\label{sec:intro_to_QO}

@@

The most basic optical quantum state comprising photons is the \textit{photon-number state}\index{Photon-number!States} or \textit{Fock state}. These states form a discrete basis, labelled by the integer number of photons in the state,
\begin{align}
\ket{n},\,n\in\mathbb{Z}^+.	
\end{align}
The special case of $\ket{0}$ is referred to as the \textit{vacuum state}\index{Vacuum state}, since it contains no photons.

@@

\subsubsection{Creation \& annihilation operators}\label{sec:creation_ann_ops}

@@

In the CV picture, instead of representing states using photonic creation operators, we express them in terms of the \textit{position} ($\hat x$)\index{Position operator} and \textit{momentum} ($\hat p$)\index{Momentum!Operator} operators, which are related to the creation and annihilation operators via,
\begin{align}
\hat x &=    \sqrt{\frac{\hbar}{2 \omega}}(\hat a + \hat a^\dag), \nonumber \\
\hat p &= -i \sqrt{\frac{\hbar  \omega}{2}}(\hat a - \hat a^\dag), 
\end{align}
where $\omega$ is the optical frequency\index{Optical!Frequency}. These operators obey the commutation relation\index{Commutation relations},
\begin{align}
[\hat x, \hat p] = i \hbar,
\end{align}
and satisfy the eigenvalue relations with the position and momentum eigenstates,
\begin{align}
\hat{x}\ket{x} &= x\ket{x},\nonumber\\
\hat{p}\ket{p} &= p\ket{p}.	
\end{align}
These eigenstates satisfy the completeness relations,
\begin{align}
\int_{-\infty}^\infty \ket{x}\bra{x}\,dx &= \hat\openone,\nonumber\\
\int_{-\infty}^\infty \ket{p}\bra{p}\,dp &	= \hat\openone.
\end{align}

The position and momentum operators represent the \textit{quadratures}\index{Quadratures} of a mode, and correspond to the real and imaginary components of a harmonic oscillator's\index{Harmonic oscillators} amplitude.

@@

\subsubsection{Position \& momentum representations}\index{Position representation}\index{Momentum!Representation}

The \textit{position representation} of an optical state corresponds to expressing a state vector $\ket{\psi}$ in the position basis\index{Position representation},
\begin{align}
\ket{\psi} = \int \psi(x)\ket{x}\, dx.
\end{align}

Here the wave-function\index{Wave-functions} in the position representation\index{Position representation} is defined as,
\begin{align}
\psi(x) = \braket{x|\psi}.
\end{align}
The state can similarly be expressed via a \textit{momentum representation}\index{Momentum!Representation},
\begin{align}
	\ket\psi = \int {\tilde\psi}(p) \ket{p}\, dp,
\end{align}s
with wave-function\index{Wave-functions},
\begin{align}
	{\tilde\psi}(p) = \braket{p|\psi},\nonumber\\
\end{align}

### 2018-12-31 Sections/models_for_quantum_computation.tex
Added authors to sections
indexing

The adiabatic theorem\index{Adiabatic!Theorem} forms the backbone of AQC, which states that for a system initially prepared in an eigenstate of a time-dependent Hamiltonian $\hat{H}(t)$, the evolution via the Schr{\"o}dinger equation\index{Schr{\"o}dinger equation},
\begin{align}
i \frac{\partial \ket{\psi(t)}}{\partial t} = \hat{H}(t)\ket{\psi(t)},
\end{align}
will keep approximately to the instantaneous ground state, if $\hat{H}(t)$ varies sufficiently slowly.

@@

Examples of adiabatic quantum algorithms include:
\begin{itemize}
\item Adiabatic Grover algorithm\index{Adiabatic!Grover algorithm}: as its name suggests, this is the adiabatic version of Grover's search algorithm. The initial Hamiltonian is,
\begin{align}
	\hat{H}_0 = \hat\openone - \ket{\phi}\bra{\phi},
\end{align}
where $\ket{\phi}$ is the uniform superposition state $\ket{+}^{\otimes n}$. The final Hamiltonian is given by,
\begin{align}
\hat{H}_1 = \hat\openone - \ket{m}\bra{m},
\end{align}
where $\ket{m}$ is the marked item we are searching for \cite{bib:PhysRevA.65.042308}.
\item Adiabatic Deutsch-Jozsa algorithm\index{Adiabatic!Deutsch-Jozsa algorithm}\index{Deutsch-Jozsa algorithm}: given a binary function,
\begin{align}
f:\{0,1 \}^n \rightarrow \{0,1\},
\end{align}
which is either constant\index{Constant functions} or balanced\index{Balanced functions}, the Deutsch-Jozsa algorithm can determine which type of function it is, exhibiting quantum speedup. An adiabatic implementation \cite{bib:PhysRevLett.95.250503} is derived to match the speedup obtained in the original circuit model implementation.
\item Adiabatic glued-trees problem\index{Adiabatic!Glued-trees problem}: here we consider two binary trees\index{Binary trees} of depth $n$. Each tree has \mbox{$2^{n+1}-1$} vertices, and the two trees are randomly glued together, as shown in Fig.~\ref{fig:glued_trees}. More specifically, a leaf is chosen from the left, is connected to a leaf on the right also chosen at random, which is then connected to another leaf on the left, and so on. Every leaf on the left is connected to two on the right and vice versa. This creates a random cycle that alternates between the two trees. The problem is to, starting from the left root, find a path to the right root in the smallest possible number of steps. Classical algorithms require at least a sub-exponential number of queries, but there exists a polynomial-time quantum algorithm based on quantum walks \cite{bib:childs2003exponential}.
\item Adiabatic \textsc{PageRank} algorithm\index{Adiabatic!PageRank algorithm}: the \textsc{PageRank}\index{PageRank algorithm} vector is a crucial tool in data mining and information retrieval, employed heavily by the Google search engine. The goal of the algorithm is to rank the importance, impact or influence of some entity in a network (webpages on the internet in the case of a Google search). The algorithm achieves this by representing the network as a flow network\index{Flow network}, whereby flow from one vertex to another represents a vote by the source vertex for the importance of the destination vertex. By finding a steady-state flow to each edge in the network, the net flow into vertices represents their cumulative importance, as determined collectively by participants in the network. However, the magnitude of votes cast by vertices is weighted by their own ranking. Therefore, the algorithm aims to filter out bogus gaming of the system via the creation of dummy nodes that cast votes en masse to rig the election. The \textsc{PageRank} approach to ranking webpages has been by far the most successful and robust such algorithm, and was perhaps the key development behind the global success of Google. The best-known classical algorithms for solving the \textsc{PageRank} problem are via: representing the flow network as a matrix equation, from which the solution is obtained via solving an eigenvalue equation; representing the flow network as a random walk, whereby walkers randomly follow paths influenced by the flows, which in the long-time limit yields walks approximating the solution. The current best-known quantum \textsc{PageRank} algorithm outperforms all currently known classical algorithms with polynomial or even exponential speedup \cite{bib:PhysRevLett.108.230506}, but better future classical algorithms have not been ruled out and are under active investigation.
\end{itemize}

>>>>

The adiabatic theorem\index{Adiabatic!Theorem} forms the backbone of AQC, which states that for a system initially prepared in an eigenstate of a time-dependent Hamiltonian $\hat{H}(t)$, the evolution via the Schr{\"o}dinger equation\index{Schr{\" o}dinger!Equation},
\begin{align}
i \frac{\partial \ket{\psi(t)}}{\partial t} = \hat{H}(t)\ket{\psi(t)},
\end{align}
will keep approximately to the instantaneous ground state, if $\hat{H}(t)$ varies sufficiently slowly.

@@

Examples of adiabatic quantum algorithms include:
\begin{itemize}
\item Adiabatic Grover algorithm\index{Adiabatic!Grover algorithm}: as its name suggests, this is the adiabatic version of Grover's search algorithm. The initial Hamiltonian is,
\begin{align}
	\hat{H}_0 = \hat\openone - \ket{\phi}\bra{\phi},
\end{align}
where $\ket{\phi}$ is the uniform superposition state $\ket{+}^{\otimes n}$. The final Hamiltonian is given by,
\begin{align}
\hat{H}_1 = \hat\openone - \ket{m}\bra{m},
\end{align}
where $\ket{m}$ is the marked item we are searching for \cite{bib:PhysRevA.65.042308}.
\item Adiabatic Deutsch-Jozsa algorithm\index{Adiabatic!Deutsch-Jozsa algorithm}\index{Deutsch-Jozsa algorithm}: given a binary function,
\begin{align}
f:\{0,1 \}^n \rightarrow \{0,1\},
\end{align}
which is either constant\index{Constant functions} or balanced\index{Balanced functions}, the Deutsch-Jozsa algorithm can determine which type of function it is, exhibiting quantum speedup. An adiabatic implementation \cite{bib:PhysRevLett.95.250503} is derived to match the speedup obtained in the original circuit model implementation.
\item Adiabatic glued-trees problem\index{Adiabatic!Glued-trees problem}: here we consider two binary trees\index{Binary trees} of depth $n$. Each tree has \mbox{$2^{n+1}-1$} vertices, and the two trees are randomly glued together, as shown in Fig.~\ref{fig:glued_trees}. More specifically, a leaf is chosen from the left, is connected to a leaf on the right also chosen at random, which is then connected to another leaf on the left, and so on. Every leaf on the left is connected to two on the right and vice versa. This creates a random cycle that alternates between the two trees. The problem is to, starting from the left root, find a path to the right root in the smallest possible number of steps. Classical algorithms require at least a sub-exponential number of queries, but there exists a polynomial-time quantum algorithm based on quantum walks \cite{bib:childs2003exponential}.
\item Adiabatic \textsc{PageRank} algorithm\index{Adiabatic!PageRank algorithm}: the \textsc{PageRank}\index{PageRank algorithm} vector is a crucial tool in data mining and information retrieval, employed heavily by the Google search engine. The goal of the algorithm is to rank the importance, impact or influence of some entity in a network (webpages on the internet in the case of a Google search). The algorithm achieves this by representing the network as a flow network\index{Flow networks}, whereby flow from one vertex to another represents a vote by the source vertex for the importance of the destination vertex. By finding a steady-state flow to each edge in the network, the net flow into vertices represents their cumulative importance, as determined collectively by participants in the network. However, the magnitude of votes cast by vertices is weighted by their own ranking. Therefore, the algorithm aims to filter out bogus gaming of the system via the creation of dummy nodes that cast votes en masse to rig the election. The \textsc{PageRank} approach to ranking webpages has been by far the most successful and robust such algorithm, and was perhaps the key development behind the global success of Google. The best-known classical algorithms for solving the \textsc{PageRank} problem are via: representing the flow network as a matrix equation, from which the solution is obtained via solving an eigenvalue equation; representing the flow network as a random walk, whereby walkers randomly follow paths influenced by the flows, which in the long-time limit yields walks approximating the solution. The current best-known quantum \textsc{PageRank} algorithm outperforms all currently known classical algorithms with polynomial or even exponential speedup \cite{bib:PhysRevLett.108.230506}, but better future classical algorithms have not been ruled out and are under active investigation.
\end{itemize}

### 2018-12-31 Sections/optical_routers.tex
Added authors to sections
indexing

\subsection{Interferometric switches} \index{Interferometric!Switches}

@@

\subsubsection{Electro-optic modulators} \index{Electro-optic modulators}

Electro-optics modulators (EOMs) are based on anisotropic materials\index{Anisotropic materials}, in which the refractive index\index{Refractive index} changes according to an applied electric field. There are two primary variations on this:
\begin{itemize}
	\item Pockel's effect\index{Pockel's effect}: a linear electro-optic effect, where the refractive index\index{Refractive index} change is proportional to the applied electric field.
	\item Kerr's effect\index{Kerr's!Effect}: a quadratic electro-optic effect, where the refractive index change is proportional to the square of the applied electric field.
\end{itemize}

@@

The refractive index of an electro-optic medium\index{Electro-optic medium} is a function $n(E)$ of the applied electric field $E$. This function varies only slightly with $E$, such that using a Taylor series expansion\index{Taylor series} about \mbox{$E=0$} we obtain,
\begin{align}
n(E) = n+a_1E + \frac{1}{2}a_2E^2+\dots.
\end{align}

In a Pockel's medium\index{Pockel's medium} this relation becomes (after approximating and simplifying),
\begin{align}
n(E) = n-\frac{1}{2}\chi n^3 E,
\end{align}
where $\chi$ is called the Pockel's coefficient\index{Pockel's coefficient} or linear electro-optic coefficient. Typical values of $\chi$ lie in the range $10^{-12}-10^{-10}$mV$^{-1}$. The most common crystals used as the medium for Pockel's cells are NH$_4$H$_2$PO$_4$ (ADP), KH$_2$PO$_4$ (KDP), LiNbO$_3$, LiTaO$_3$, and CdTe.

@@

\begin{figure}[!htbp]
\includegraphics[clip=true, width=0.475\textwidth]{pockels_medium} \if 2\pubmode \\ \fi
\includegraphics[clip=true, width=0.475\textwidth]{kerrs_medium}
\captionspacefig \caption{Dependence of refractive index on electric field in: Pockel's medium\index{Pockel's medium}, exhibiting linear electric field dependence; Kerr's medium\index{Kerr's!Medium}, exhibiting quadratic electric field dependence. Graphs express qualitative behaviour only, hence no numbers are provided.}\label{fig:EOM_ref_index}
\end{figure}

>>>>

\subsection{Interferometric switches} \index{Interferometric!Switches}\label{sec:interfer_switches}

\sectionby{Rohit Ramakrishnan}

@@

\subsubsection{Electro-optic modulators} \index{Electro-optic!Modulators}

Electro-optics modulators (EOMs) are based on anisotropic materials\index{Anisotropic materials}, in which the refractive index\index{Refractive index} changes according to an applied electric field. There are two primary variations on this:
\begin{itemize}
	\item Pockel's effect\index{Pockel's!Effect}: a linear electro-optic effect, where the refractive index\index{Refractive index} change is proportional to the applied electric field.
	\item Kerr's effect\index{Kerr's!Effect}: a quadratic electro-optic effect, where the refractive index change is proportional to the square of the applied electric field.
\end{itemize}

@@

The refractive index of an electro-optic medium\index{Electro-optic!Medium} is a function $n(E)$ of the applied electric field $E$. This function varies only slightly with $E$, such that using a Taylor series expansion\index{Taylor series} about \mbox{$E=0$} we obtain,
\begin{align}
n(E) = n+a_1E + \frac{1}{2}a_2E^2+\dots.
\end{align}

In a Pockel's medium\index{Pockel's!Medium} this relation becomes (after approximating and simplifying),
\begin{align}
n(E) = n-\frac{1}{2}\chi n^3 E,
\end{align}
where $\chi$ is called the Pockel's coefficient\index{Pockel's!Coefficient} or linear electro-optic coefficient. Typical values of $\chi$ lie in the range $10^{-12}-10^{-10}$mV$^{-1}$. The most common crystals used as the medium for Pockel's cells are NH$_4$H$_2$PO$_4$ (ADP), KH$_2$PO$_4$ (KDP), LiNbO$_3$, LiTaO$_3$, and CdTe.

@@

\begin{figure}[!htbp]
\includegraphics[clip=true, width=0.475\textwidth]{pockels_medium} \if 2\pubmode \\ \fi
\includegraphics[clip=true, width=0.475\textwidth]{kerrs_medium}
\captionspacefig \caption{Dependence of refractive index on electric field in: Pockel's medium\index{Pockel's!Medium}, exhibiting linear electric field dependence; Kerr's medium\index{Kerr's!Medium}, exhibiting quadratic electric field dependence. Graphs express qualitative behaviour only, hence no numbers are provided.}\label{fig:EOM_ref_index}
\end{figure}
